Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-17 demystify.tex
updates

\newcommand{\chapterinfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{chapterinfo}{\color{black}{\emph{#1}}}%
}
\newcommand{\sectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{sectioninfo}{\color{black}{\emph{#1}}}%
}
\newcommand{\subsectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{subsectioninfo}{\color{black}{\texttt #1}}%
}

@@

\chapter{Letters of Recommendation (LoR)}\label{chap:lor}
\chapterinfo{LORs are very important, but only if they are personalized and talk about your research ability.}

@@

\chapter{Research Experience}\label{chap:research-experience}
\chapterinfo{Publications can greatly help. Papers in good venues are concrete evidence that you have successfully engaged in research. But they are not required!}

@@

\section{Competitions} Winning \emph{internationally recognized competitions} can demonstrate your research potential.
For example, participating in Math Olympiads if you want to do theory or winning ACM programming contests if you want to ``build'' systems, e.g., software analysis.

\chapter{Statement of Purpose (SOP)}\label{chap:sop}
\chapterinfo{SOP is important. Write it in such a way that makes you \emph{stand out}.}

@@

\chapter{Standard Tests (GRE and IELTS)}\label{chap:standard-tests}
\chapterinfo{Standard tests are not important. GRE typically \emph{is not} required. For standard English tests (not required for domestic students), just do enough to pass the minimum requirements.}

>>>>

\newcommand{\chapterinfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{chapterinfo}{\textcolor{black}{\emph{#1}}}%
}
\newcommand{\sectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{sectioninfo}{\textcolor{black}{\emph{#1}}}%
}
\newcommand{\subsectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{subsectioninfo}{\textcolor{black}{\texttt #1}}%
}

@@

\chapter{Letters of Recommendation (LoR)}\label{chap:lor}
\chapterinfo{LORs are very important, but only if they are \textbf{personalized} and \textbf{research focused}.}

@@

\chapter{Research Experience}\label{chap:research-experience}
\chapterinfo{Publications are not \textbf{required} but can \textbf{greatly help}. Papers in good venues are concrete evidence that you have successfully engaged in research.}

@@

\section{Competitions} Winning \emph{internationally recognized competitions} can demonstrate your research potential.
For example, participating in Math Olympiads if you want to do theory or winning ACM programming contests if you want to ``build'' systems, e.g., software analysis.  
So do talk about them in your SOP (\autoref{chap:sop}) and have your LoR writers mention them in their letters (\autoref{chap:lor}).

\chapter{Statement of Purpose (SOP)}\label{chap:sop}
\chapterinfo{SOP is important. Write it in such a way that makes you \textbf{stand out}.}

@@

\chapter{Standard Tests (GRE and IELTS)}\label{chap:standard-tests}
\chapterinfo{Standard tests are \textbf{not} important. GRE typically \emph{is not} required. For standard English tests (not required for domestic students), just do enough to pass the minimum requirements.}
